sdmTMB: an R package for fast, flexible, and user-friendly generalized linear mixed effects models with spatial and spatiotemporal random fields

### 2022-11-02 doc/paper-jss/owls.Rmd
Checkmarks and x's

```
#>   Non-linear minimizer suggests successful convergence
#>   Hessian matrix is positive definite
#>   No extreme or very small eigen values detected
#> x `ln_tau_E` gradient > 0.001
#>   See `?run_extra_optimization()`
#>   Or refit with `control = sdmTMBcontrol(newton_loops = 1)`
#> 
#> x `ln_phi` gradient > 0.001
#>   See `?run_extra_optimization()`
#>   Or refit with `control = sdmTMBcontrol(newton_loops = 1)`
#> 
#>   No fixed-effect standard errors are NA
#>   No fixed-effect standard errors look unreasonably large
#>   No sigma parameters are < 0.01
#>   No sigma parameters are > 100
#>   Range parameter doesn't look unreasonably large
```

@@

```
#> Non-linear minimizer suggests successful convergence
#> Hessian matrix is positive definite
#> No extreme or very small eigen values detected
#> No gradients with respect to fixed effects are >= 0.001
#> No fixed-effect standard errors are NA
#> No fixed-effect standard errors look unreasonably large
#> No sigma parameters are < 0.01
#> No sigma parameters are > 100
#> Range parameter doesn't look unreasonably large
```

>>>>

```
#> ✓ Non-linear minimizer suggests successful convergence
#> ✓ Hessian matrix is positive definite
#> ✓ No extreme or very small eigen values detected
#> ✗ `ln_tau_E` gradient > 0.001
#>   See `?run_extra_optimization()`
#>   Or refit with `control = sdmTMBcontrol(newton_loops = 1)`
#> 
#> ✗ `ln_phi` gradient > 0.001
#>   See `?run_extra_optimization()`
#>   Or refit with `control = sdmTMBcontrol(newton_loops = 1)`
#> 
#> ✓ No fixed-effect standard errors are NA
#> ✓ No fixed-effect standard errors look unreasonably large
#> ✓ No sigma parameters are < 0.01
#> ✓ No sigma parameters are > 100
#> ✓ Range parameter doesn't look unreasonably large
```

@@

```
#> ✓ Non-linear minimizer suggests successful convergence
#> ✓ Hessian matrix is positive definite
#> ✓ No extreme or very small eigen values detected
#> ✓ No gradients with respect to fixed effects are >= 0.001
#> ✓ No fixed-effect standard errors are NA
#> ✓ No fixed-effect standard errors look unreasonably large
#> ✓ No sigma parameters are < 0.01
#> ✓ No sigma parameters are > 100
#> ✓ Range parameter doesn't look unreasonably large
```
